### 2023-01-19 doc/src/IPIs.tex
Warn about need for FENCE before software sends an MSI as an IPI
Signed-off-by: John Hauser <31252952+jhauser-us@users.noreply.github.com>

>>>>

\begin{commentary}
When software sends IPIs by writing MSIs to the IMSICs of other
harts, programmers should consider also the need to execute a FENCE
instruction before each store instruction that writes such an MSI.
In the absence of FENCEs, many systems guarantee to preserve the
order of a hart's loads and stores only to/from individual devices,
not among multiple devices, and not at all for accesses to main memory.
With such a system, it must be remembered that each IMSIC
is likely to be considered a separate device among the many.
For example, if hart~A wants to notify hart~B that it has
completed a task involving accesses to some I/O device,
hart~A may need to execute a FENCE before sending an MSI to
B's IMSIC, to ensure that all of A's accesses to the device
have actually completed before the MSI could arrive at B.
Similarly, if hart~A stores anything to memory that
should be visible at hart~B, a FENCE is likely needed
before a subsequent store sending an MSI to B's IMSIC.
\end{commentary}
